Oregon_Wildfire_reduced

### 2017-02-27 r_scripts/oregon_clean.rmd
Update oregon_clean.rmd

>>>>

## How many visits does unique personkey have?
```{r}
visit <- oregon_df %>%
  select(personkey, clmid) %>%
  mutate(num_visit = NA)

for (i in 1: length(oregon_df$personkey)){
  visit$num_visit[i] <- length(unique(visit$clmid[which(visit$personkey==visit$personkey[i])]))

}

a<-unique(oregon_df$personkey)

visit2 <- visit %>%
  select(personkey, num_visit) %>%
  distinct(personkey, num_visit)

visit3 <- visit2 %>%
  group_by(num_visit) %>%
  summarise(n = n()) %>%
  mutate(total_n =sum(n),
  percent = round(n/total_n, 4)*100) %>% 
  select(num_visit, n, percent)

m <- mean(visit2$num_visit)
median(visit2$num_visit)
m # 4.61

knitr::kable(visit3, align = "c", caption = "Visits")

hist(visit3$num_visit, br= 20)

ggplot(visit3, aes(x=num_visit)) +
  geom_density()
